---
title: "Module 5 - Hollywood’s Most Profitable Stories"
author: "Fariha Khan"
date: "August 25 2019"
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction
This analysis explores Hollywood's Most Profitable Stories dataset to conduct statistical hypothesis testing.

Data was loaded downloaded from the sample data available on https://public.tableau.com/en-us/s/resources.


Use the following packages for hypothesis testing:
```{r}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(ggpubr))
suppressPackageStartupMessages(library(knitr))
```


Read in data
```{r}
df <- read.csv("~/Documents/MS_DataScience/MIS500/Week5/data/HollywoodsMostProfitableStories.csv")
glimpse(df)
```

Clean up dataset

 - Clean column

 - Remove NA
 
```{r}
names(df)
df <- df %>% 
      rename(Audience.score = Audience..score.., 
             Rotten.Tomatoes = Rotten.Tomatoes..) %>%
      mutate(Film = as.character(Film)) %>% 
      na.omit()
glimpse(df)
```


# Preliminary Testing

Check distribution of variables

```{r densityplots, echo=TRUE}
xdens <- ggdensity(df, x = "Audience.score",add = "mean", 
                   title = "Audience Score Density") +
      stat_overlay_normal_density(color = "red", linetype = "dashed")

ydens <- ggdensity(df, x = "Worldwide.Gross", add = "mean", 
                   title = "Worldwide Gross Density") +
      stat_overlay_normal_density(color = "blue", linetype = "dashed")

ggarrange(xdens, ydens, labels = "AUTO")
```


Do Shapiro-Wilk normality test and draw quantile-quantile plots

```{r normalityTest}
xshap <- shapiro.test(df$Audience.score) %>% 
      unlist() %>% t() %>% as.data.frame()
xshap <- xshap[2]
xshap <- ggtexttable(xshap, cols = colnames(xshap))
xq <- ggqqplot(df$Audience.score, color = "red", size = 1, shape = 1,
               ylab = "Audience Score (%)")

yshap <- shapiro.test(df$Worldwide.Gross) %>% 
      unlist() %>% t() %>% as.data.frame()
yshap <- yshap[2]
yshap <- ggtexttable(yshap, cols = colnames(yshap))
yq <- ggqqplot(df$Worldwide.Gross, color = "blue", size = 1, 
               shape = 1, ylab = "Worldwide Gross")
ggarrange(xshap, yshap, xq, yq, 
          ncol = 2, nrow = 2, heights = c(1, 3), labels = c("A", "B"))
```


# Correlation tests
```{r scatterplots}

ggscatter(df, x = "Audience.score", y = "Worldwide.Gross", 
          add = "reg.line", conf.int = TRUE, cor.coef = TRUE, 
          title = "Audience Score vs. Worldwide Gross",
          cor.method = "spearman")

ggscatter(df, x = "Audience.score", y = "Worldwide.Gross", 
          add = "reg.line", conf.int = TRUE,
          cor.coef = TRUE, cor.method = "kendall",
          title = "Audience Score vs. Worldwide Gross")

```

```{r}

x <- cor.test(x = df$Audience.score, y = df$Worldwide.Gross,
          method = "spearman", alternative = 'greater')

cor.test(x = df$Audience.score, y = df$Worldwide.Gross,
          method = "kendall")
```

